---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# meangirls

<!-- badges: start -->
<!-- badges: end -->

The goal of meangirls is to create quotes in the style of the
2004 instant classic movie, *Mean Girls*.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

```{r}
#library(devtools)
#devtools::install_github("Cal-Poly-Advanced-R/meangirls")
```

```{r}
library(meangirls)
```


## insults

You can use the function `boo()` to deliver a generic insult:

```{r}
boo("jerk")
```

You can use the function `fetch()` to insult someone's made-up slang word.

```{r}
fetch("Gretchen", "fetch")
```


## compliments

You can use the function `nice_style()` to compliment someone's fashion choices.  
The default adjective is "vintage", but you can supply your own.

```{r}
nice_style("bracelet")

nice_style("bracelet", adjective = "colorful")
```


You can use the function `really_pretty()` to tell someone they are pretty.

```{r}
really_pretty("Cady", follow_up = FALSE)
```

### Negating compliments

Both compliments can be negated with a follow-up phrase:

```{r}
really_pretty("Cady", follow_up = TRUE)
nice_style("bracelet", follow_up = TRUE)
```


## Handing out candygrams

Finally, you can use the `give_candygrams()` function to announce the number of
candygrams a person gets.

```{r}
give_candygrams("Taylor Zimmerman", 2)
```

### Extra comments

You can also give extra commentary to your announcement:

```{r}
give_candygrams("Taylor Zimmerman", 2, 
                extra_message = "Merry Christmas!")
```


Some special cases trigger automatic extra commentary or special behavior:


```{r}
give_candygrams("Glen Coco", 4)
```

```{r}
give_candygrams("Gretchen Weiners", 4)
```


